\chapter{Future stuff}
Look at algorithms that focus more on object detection while doing style transfer for the found objects.
Are a better way to detect feature maps.
Either way a two step algorithm that first detects objects and maps the style for each object.
Iets dat zoekt naar gelijkaarde objecten in two afbeeldingen en daarop de stijl toepast.
Dit algorithme heeft dan gelijkaarde objecten in beide afbeeldingen nodig om goed te werken.
Je ziet dat dit bij de meest recente unsupervised algoritmes al the geval is, waar ze enkel close-ups in de dataset gaan steken.


(dirty version)
(StyleGAN) Because I feel that the images to be trained on are not genre or artist dependent, because there is still a high variety among them.
I think that it should be possible to train a style transfer with only a few samples.
It was said to me that StyleGAN did this.
I also want to research diffusion.

Augmentatie aan de hand van 3d modellen die met verschillende shaders worden gerenderd, of worden vervormd door gekend algorithme om zo de transformatie te achterhalen.

Should train model on Human-Art or see if there can be found one somewhere.

When training a top-down estimator, then how does it make a destinction between people in a bounding box that are in the background?
How many people will it find that way?

A object detection model should be able to tell when two objects are similar without having labels.
It should categorize purely on the attributes.
You know, like a cluster algorithm or something.



Discuss Tuiring completeness of transformers